Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-07-15 paper/paperv3.qmd

missing_seals %>% 
  group_by(age) %>% 
  summarize(n = n(),
            n_unobserved = sum(unobserved),
            unobserved_mean = n_unobserved / n,
            unobserved_lwr = binom.test(n_unobserved, n)$conf.int[1],
            unobserved_upr = binom.test(n_unobserved, n)$conf.int[2]) %>% 
  ggplot(aes(age)) +
  geom_line(aes(y = predicted, group = year_fct), 
            missing_pred_years, 
            alpha = 0.2) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high),
              missing_pred,
              alpha = 0.2,
              fill = "#de77ae") +
  geom_line(aes(y = predicted),
            missing_pred,
            color = "#de77ae",
            linewidth = 2) +
  geom_pointrange(aes(y = unobserved_mean, 
                      ymin = unobserved_lwr, ymax = unobserved_upr)) +
  scale_x_continuous("Age", breaks = seq(5, 19, by = 4)) +
  scale_y_continuous("Unobserved proportion", 
                     labels = scales::label_percent(accuracy = 1),
                     limits = c(0, NA))
```

>>>>

missing_pred_pop <- tibble(age = 5:19,
                           age10 = (age - age_senesce) / 10) %>% 
  mutate(predicted = predict(missing_mod, 
                             newdata = .,
                             type = "response",
                             re.form = NA))
missing_seals %>% 
  group_by(age) %>% 
  summarize(n = n(),
            n_unobserved = sum(unobserved),
            unobserved_mean = n_unobserved / n,
            unobserved_lwr = binom.test(n_unobserved, n)$conf.int[1],
            unobserved_upr = binom.test(n_unobserved, n)$conf.int[2]) %>% 
  ggplot(aes(age)) +
  geom_line(aes(y = predicted, group = year_fct), 
            missing_pred_years, 
            alpha = 0.2) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high),
              missing_pred,
              alpha = 0.2,
              fill = "#de77ae") +
  geom_line(aes(y = predicted),
            missing_pred,
            color = "#de77ae",
            linewidth = 2) +
  geom_line(aes(y = predicted),
            missing_pred_pop,
            linewidth = 1.5,
            linetype = "dotted",
            alpha = 0.5) +
  geom_pointrange(aes(y = unobserved_mean, 
                      ymin = unobserved_lwr, ymax = unobserved_upr)) +
  scale_x_continuous("Age", breaks = seq(5, 19, by = 4)) +
  scale_y_continuous("Unobserved proportion", 
                     labels = scales::label_percent(accuracy = 1),
                     limits = c(0, NA))
```
